PM Mungbean meta-analysis

### 2020-06-22 02_Preliminary_analysis.Rmd
We're mitigating yield loss, not yield
Add labels to graphs, Markdown syntax edits

#### Timing of fungicide sprays  
The timing of fungicide application can be crucial for maximum disease control and yield mitigation. 
The experiments all relied on natural infection and thus infection at a standardised crop maturity stage was not possible. 
To best estimate the effect of fungicide application timing we will use the day when the disease was first found in the field as a reference.
The first sign of disease is a useful reference as it can be assessed with little training for the assessor.

@@

```{r spray_relative2FS}
PM_MB_means %>%
   mutate(
      s1_DfromFS = fungicide_application_1 - first_sign_disease,
      s2_DfromFS = fungicide_application_2 - first_sign_disease,
      s3_DfromFS = fungicide_application_3 - first_sign_disease,
      s4_DfromFS = fungicide_application_4 - first_sign_disease,
      s5_DfromFS = fungicide_application_5 - first_sign_disease
   ) %>%
   gather(
      key = spray,
      value = n_days,
      s1_DfromFS,
      s2_DfromFS,
      s3_DfromFS,
      s4_DfromFS,
      s5_DfromFS
   ) %>%
   drop_na(n_days) %>% 
   ggplot(aes(x = spray, y = as.numeric(n_days))) +
   geom_violin() +
   scale_x_discrete(
      labels = c(
         "First spray",
         "Second spray",
         "Third spray",
         "Fourth spray",
         "Fifth spray"
      )
   ) +
   ylab("Days to First Sign of Disease")+
   facet_grid(cols = vars(total_fungicide)) +
   coord_flip()
```

@@

### Mungbean cultivars  
In general, mungbean varieties have the following resistance to powdery mildew.

@@

```{r yield_vol}
# Outputs the table and graph
source("R/yield_volatility.r") # function to investigate the volatility in yields
# Volatility is the range between the upper and lower 97.5 and 2.5 % quartiles

YV1 <-
   yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
YV1[[2]] + 
   scale_fill_usq()

YV1[[3]]
```

This plot shows a large amount of yield volatility in all cultivars except Green Diamond.
Green Diamond shows little volatility probably because this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trial.

@@

There still remains a higher volatility in Jade and perhaps a greater shift in the probability curve including fungicide treatments vs probability curves including only no spray controls.
Indicating that there might be a difference in powdery mildew tolerance between Jade and Crystal.

Overall there seems to be an influence of cultivar however this variation is not as distinct as the variation between trials.

@@

Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease.
The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows in most cases increased yield significantly.
This finding has also been shown by several other researchers' work in Queensland and New South Wales as well.
Eight trials used a row spacing of 0.75&nbsp;meters and tebuconazole as an active ingredient (AI).

@@

```{r RS_severity}
# Which row spacing leads to the higher disease severity
PM_MB_means %>%
   filter(year == 2017 |
             year == 2018) %>%
   filter(fungicide_ai == "control") %>%
   ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
   ggtitle("Powdery mildew variation between different row spacing")
```

@@

```{r RS_yield}
# Which row spacing leads to the higher yield potential
PM_MB_means %>%
   filter(year == 2017 |
             year == 2018) %>%
   ggplot(aes(
      y = as.numeric(grain_yield.t.ha.),
      x = row_spacing,
      colour = location
   )) +
   geom_jitter(width = 0.01) +
   ggtitle("Grain yield results for different row spacing at three locations") +
   xlab("Row spacing (m)") +
   ylab("Grain yield (t/ha)") +
   scale_colour_usq()
```

@@

Overall row spacing may influence both powdery mildew severity and yield.

>>>>

#### Timing of fungicide sprays  
The timing of fungicide application can be crucial for maximum disease control and yield loss mitigation. 
The experiments all relied on natural infection and thus infection at a standardised crop maturity stage was not possible. 
To best estimate the effect of fungicide application timing we will use the day when the disease was first found in the field as a reference.
The first sign of disease is a useful reference as it can be assessed with little training for the assessor.

@@

```{r spray_relative2FS}
PM_MB_means %>%
   mutate(
      s1_DfromFS = fungicide_application_1 - first_sign_disease,
      s2_DfromFS = fungicide_application_2 - first_sign_disease,
      s3_DfromFS = fungicide_application_3 - first_sign_disease,
      s4_DfromFS = fungicide_application_4 - first_sign_disease,
      s5_DfromFS = fungicide_application_5 - first_sign_disease
   ) %>%
   gather(
      key = spray,
      value = n_days,
      s1_DfromFS,
      s2_DfromFS,
      s3_DfromFS,
      s4_DfromFS,
      s5_DfromFS
   ) %>%
   drop_na(n_days) %>%
   ggplot(aes(x = spray, y = as.numeric(n_days))) +
   geom_violin() +
   scale_x_discrete(labels = c(
      "First spray",
      "Second spray",
      "Third spray",
      "Fourth spray",
      "Fifth spray"
   )) +
   ylab("Days to First Sign of Disease") +
   facet_grid(cols = vars(total_fungicide)) +
   coord_flip()
```

@@

### Mungbean cultivars

Australian mungbean varieties have the following resistance to powdery mildew.

@@

```{r yield_vol}
# Outputs the table and graph
source("R/yield_volatility.r") # function to investigate the volatility in yields
# Volatility is the range between the upper and lower 97.5 and 2.5 % quartiles
YV1 <-
   yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
YV1[[2]] + 
   scale_fill_usq()
YV1[[3]]
```

This plot shows a large amount of yield volatility in all cultivars except Green Diamond.
Green Diamond shows little volatility probably because this cultivar was only used in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trial.

@@

There still remains a higher volatility in Jade and perhaps a greater shift in the probability curve including fungicide treatments versus probability curves including only no spray controls.
Indicating that there might be a difference in powdery mildew tolerance between Jade and Crystal.

Overall there seems to be an influence of cultivar.
However this variation is not as distinct as the variation between trials.

@@

Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease as well as fungicide timing and efficacy.
The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows in most cases increased yield significantly.
This finding has also been shown by several other researchers' work in Queensland and New South Wales as well.
Eight trials used a row spacing of 0.75&nbsp;meters and tebuconazole as an active ingredient (AI).

@@

```{r RS_severity}
# Which row spacing leads to the higher disease severity
PM_MB_means %>%
   filter(year == 2017 |
             year == 2018) %>%
   filter(fungicide_ai == "control") %>%
   ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
   ylab("Final severity rating") +
   xlab("Row spacing (m)") +
   ggtitle("Powdery mildew variation between different row spacing")
```

@@

```{r RS_yield}
# Which row spacing leads to the higher yield potential
PM_MB_means %>%
   filter(year == 2017 |
             year == 2018) %>%
   ggplot(aes(
      y = as.numeric(grain_yield.t.ha.),
      x = as.factor(row_spacing),
      colour = location
   )) +
   geom_jitter(width = 0.1) +
   ggtitle("Grain yield results for different row spacing at three locations") +
   xlab("Row spacing (m)") +
   ylab("Grain yield (t/ha)") +
   scale_colour_usq()
```

@@

Overall row spacing may influence both powdery mildew severity and yield.
However, in the studies that were conducted, no interaction was found between row spacing, powdery mildew severity and yield.
That is, the row spacing appeared to increase yield even if the amount of powdery mildew increased and no relationship could be detected between an interaction of the three.
